B\'{e}zier $\bar{B}$ projection

### 2018-02-14 projection1120.tex
Revisions.

\begin{abstract}
  We demonstrate the use of B\'{e}zier projection to alleviate locking phenomena in structural mechanics applications of isogeometric analysis. \added{Based on two different 	
  interpretations of the well-known $\bar{B}$ projection, we propose two formulations and name them symmetric and non-symmetric B\'{e}zier $\bar{B}$ projection.} To demonstrate the utility of the \added{\Bezier projection} for both geometry and material locking phenomena we focus on transverse shear locking in Timoshenko beams and volumetric locking in nearly compressible linear elasticity although the approach can be applied generally to other types of locking phenemona as well. B\'{e}zier projection is a local projection technique with optimal approximation properties, which in many cases produces solutions that are comparable to global $L^2$ projection. In the context of $\bar{B}$ methods, the use of B\'ezier projection produces sparse stiffness matrices with only a slight increase in bandwidth when compared to standard displacement-based methods. Of particular importance is that the approach is applicable to any spline representation that can be written in B\'ezier form like NURBS, T-splines, LR-splines, etc. We discuss in detail how to integrate this approach into an existing finite element framework with minimal disruption through the use of B\'ezier extraction operators and a newly introduced dual \added{basis for} \Bezier \added{projection} operator. We then demonstrate the behavior of the two proposed formulations through several challenging benchmark problems.
\end{abstract}
\keywords{Isogeometric analysis, B\'ezier extraction, \added{\Bezier dual basis}, B\'ezier projection, $\bar{B}$-projection, locking}
\section{Introduction}
Isogeometric analysis (IGA), introduced by Hughes et al. \cite{hughes_isogeometric_2005}, adopts the spline basis, which underlies the CAD geometry, as the basis for analysis. Of particular importance is the positive impact of smoothness on numerical solutions, where, in many application domains, IGA outperforms classical finite elements~\cite{cottrell_isogeometric_2009,cottrell_studies_2007,cottrell2006isogeometric,hughes_duality_2008,bazilevs_isogeometric_2010,evans_n-widths_2009}. Initial investigations of IGA focused on non-uniform rational B-splines (NURBS) due to their dominance in commercial CAD packages. However, many advances are being made in analysis-suitable geometry representations that overcome the strict rectangular topological restrictions of NURBS. Examples include T-splines~\cite{bazilevs_isogeometric_2010,sederberg_t-splines_2003} and their analysis-suitable restriction~\cite{scott_local_2012, li_analysis-suitable_2013}, hierarchical B-splines~\cite{bornemann_subdivision-based_2013,scott_isogeometric_2014,schillinger_isogeometric_2012,evans_hierarchical_2015,forsey_hierarchical_1988}, and locally refined B-splines~\cite{dokken_polynomial_2013,johannessen_isogeometric_2014} among others.

@@

\added{In this paper we introduce two methods that employ \Bezier projection to increase the sparsity of the stiffness matrix that results form $\bar{B}$ methods, which typically lead to a dense system. We call these methods the symmetric and non-symmetric \Bezier $\bar{B}$ projection methods based on the resulting symmetry of the stiffness method. We show that both methods result in a sparse stiffness matrix, reduce locking, and result in optimal (non-symmetric method) or near optimal (symmetric method) convergence rates.  We also perform an inf-sup analysis to help provide further insight into the behavior and quality of these methods.}

@@

The element-wise projection produces one control value for each element in the support of the function.  These values must be combined in order to provide the final control value.  A core component of the B\'ezier projection algorithm is the definition of an appropriate averaging operation. \added{The process of computing weights is illustrated in Figure~\ref{fig:weights}.} A weighted average of the values is computed using the weighting
\begin{equation}\label{eqn:Bezier_weight}
\omega_a^e=\dfrac{\int_{\Omega^e} N_{a}^e \, d\Omega}{\int_{\Omega^A} N_{A(e,a)} \, d\Omega}
\end{equation}
where $\Omega^e$ corresponds to the physical domain of element $e$, $A(e,a)$ is a mapping from a local nodal index $a$ defined over element $e$ to a corresponding global node index $A$, and $\Omega^A$ corresponds to the physical support of $N_A$. The final averaged global control point is then calculated as
\begin{equation}
P_A=\sum_{\Omega^e\in \Omega^A } \omega_{A(e,a)} P_{A(e,a)}.
\end{equation}
B\'ezier projection onto NURBS functions can be defined in an analogous manner~\cite{thomas_bezier_2015}.

@@

\subsection{Dual basis formulation of B\'{e}zier projection}
\label{sec:dual-funct-dual}
To integrate \Bezier projection into a standard finite element assembly algorithm, it is convenient to recast \Bezier projection in terms of a dual basis. \added{This approach plays a key role in developing the non-symmetric \Bezier $\bar{B}$ method discussed in Section~\ref{sec:non-symmetric}.} A dual basis has the distinguishing property that
\begin{align}
  \int_{\Omega} \hat{N}_A N_B \, d\Omega = \delta_{AB}.
  \end{align}
Once a dual basis is defined it can be processed in much the same manner as standard basis functions are processed in a finite element code. A complete exposition on the subject of dual bases and the \Bezier projection framework can be found in~\cite{thomas_bezier_2015}. We first define the dual element extraction operator
\begin{align}
 \hat{\mathbf{D}}^e=\operatorname{diag}({\boldsymbol{\omega}^e})\mathbf{R}^e(\mathbf{G}^e)^{-1}
\end{align}
where $\mathbf{G}^e$ is the Gramian matrix of the Bernstein basis functions over the element and $\operatorname{diag}({\boldsymbol{\omega}^e})$ is a diagonal matrix that contains the B\'ezier projection weights computed by (\ref{eqn:Bezier_weight}). We can then define a dual basis function $\hat{N}_{A(e,a)}$ restricted to element $e$ as
\begin{align}
\hat{N}^e_{a} = \sum_{j}\hat{D}_{aj}^e B_{j}.
\label{eq:local-dual-basis}
\end{align}

@@

\subsection{Symmetric \Bezier $\bar{B}$ projection}
\label{sec:symmetric-projection}
{\color{blue}For the Timoshenko beam, it is the transverse shear that causes locking. Hence, under the framework of $\bar{B}$ projection, the shear strain $\gamma$ is projected onto a lower order function space. The projected shear strain $\bar{\gamma}$ is used when solving the strain energy minimization problem. Here we use the \Bezier projection operator to obtain $\bar{\gamma}$, and refer to it as the Symmetric \Bezier $\bar{B}$ projection method because the resulting stiffness matrix is symmetric.}

@@

\subsubsection{Discretization}
\added{We discretize $\omega$ and $\phi$ as}
\begin{align}
  \added{\omega = \sum_A \omega_A N_A} \\
  \added{\phi = \sum_A \phi N_A}
\end{align}
where \added{$N_A$ is a degree $p$ spline basis function, $\omega_A$ and $\phi_A$ are the corresponding control point values.}. \added{The shear strain and bending strain can then be expressed as}
{\color{blue}\begin{align}
\gamma &= \sum_A{\begin{bmatrix}N'_A & -N_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T} \\
\kappa &= \sum_A\begin{bmatrix}0 & N'_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T
\end{align}}
The shear strain $\bar{\gamma}$ is constructed by B\'{e}zier projection of the true shear strain $\gamma$ onto a lower degree space. In other words, we project from a $p^{th}$ degree spline space with $n$ basis functions $\mathbf{N}$ defined by the knot vector
\begin{align}
\mathbf{\Xi}_{p}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p+1$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p+1$ copies}}\rbrace,
\label{eq:origin_knot_vector}
\end{align}
onto a $p-1^{th}$ degree spline space with $\bar{n}$ basis functions $\bar{\mathbf{N}}$ defined by the knot vector
\begin{equation}
\bar{\mathbf{\Xi}}_{p-1}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p$ copies}}\rbrace
\label{eq:projected_knot_vector}
\end{equation}
where the internal knots, denoted by $\mathbf{\Xi}_{int}$, are the same for both spaces. The projected shear strain $\bar{\gamma}$ can then be written as
\begin{align}
  \bar{\gamma} &= \sum_A \bar{\gamma}_A \bar{N}_A.
\end{align}
The control variables $\bar{\gamma}_A$ are simply
\begin{align}
  \bar{\gamma}_A = \int_{\Omega^A} \hat{\bar{N}}_A \gamma \, d\Omega = \langle \hat{\bar{N}}_A, \gamma \rangle_{\Omega^i}
\end{align}
where $\hat{\bar{N}}_A$ is a dual basis function for the spline space of degree $p-1$ computed from \eqref{eq:local-dual-basis}.

@@

\added{The relationship between $\bar{B}$-formulations and mixed formulations has been studied and it has been shown by Simo and Hughes \cite{hughes_variational_1986} that they are equivalent. However, the symmetric \Bezier $\bar{B}$ projection method presented in Section~\ref{sec:symmetric-projection}, where we started by considered the $\bar{B}$ formulation as a strain projection method, lacks this connection to mixed formulations (we will show this in the following section). In this section we present a second method based on \Bezier projection in which we view the $\bar{B}$ formulation as a mixed formulation with the auxiliary variable (the shear stress for the case of Timoshenko beam) being eliminated. Taking advantage of the dual basis formulation of the \Bezier projection operator we can incorporate \Bezier projection into the mixed formulation by using the \Bezier dual basis functions as the test functions of the auxiliary variable. Since the resulting stiffness matrix is not symmetric, this formulation is referred to as the non-symmetric \Bezier $\bar{B}$ projection method. Although this method does not preserve symmetry we will show that it does preserve convergence rates.}
\subsubsection{The weak form}
\added{In the mixed formulation, the shear stress $\tau=sGA\gamma$ is taken as a new independent variable. The weak form of the mixed formulation is then of the following form: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ and $\tau\in{L}^2(\Omega)$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$ and $\delta\tau\in{L}^2(\Omega)$}
\begin{align}
    \int_{0}^L\kappa(\mathbf{w})EI\kappa(\mathbf{u}) + {\gamma}(\mathbf{w})\tau \, dx&= l\langle{\mathbf{w}}\rangle\\
    \int_{0}^L\delta\tau(sGA\gamma(\mathbf{u})-\tau) \, dx &= 0.
\end{align}
\subsubsection{Discretization}
\added{In the finite element formulation of the mixed form, the discretization of $\mathbf{u}$ and $\mathbf{w}$ remain the same. Since the shear strain and its variation are in $L^2(\Omega)$, their finite element approximation can be made from functions with poor regularity e.g. discontinuous polynomials. For consistency, if the field $\mathbf{u}$ is discretized by $p^{th}$ degree spline  basis functions defined by the knot vector \eqref{eq:origin_knot_vector}, the shear stress $\tau$ is then discretized by $p-1^{th}$ degree spline basis functions defined by the knot vector \eqref{eq:projected_knot_vector} and its variation $\delta\tau$ is discretized by the corresponding dual basis functions, as}
\begin{align}
    \tau&=\sum_A\tau_A\bar{N}_A \\
    \delta\tau&=\sum_A\delta\tau_A\hat{\bar{N}}_A
\end{align}
\added{The stiffness matrix for the mixed form can be written as}
\begin{equation}
   \mathbf{K}_{mix} =  
    \begin{bmatrix}
        \mathbf{K}^b & \mathbf{P}^T \\
        sGA\hat{\mathbf{P}} & -\mathbf{I}
    \end{bmatrix}
    \label{eq:mixed_timoshenko}
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e,
\end{equation}
with
\begin{equation}
    \mathbf{P}_e=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
\added{The control variable of shear stress in \eqref{eq:mixed_timoshenko} can be eliminated, which leads to a pure displacement formulation as}
\begin{equation}
    \mathbf{K}=\mathbf{K}^b+\bar{\mathbf{K}}^s_{NS}, 
\end{equation}
where 
\begin{equation}
    \bar{\mathbf{K}}^s_{NS}=sGA\mathbf{P}^T\hat{\mathbf{P}}.
    \label{eq:nonsymmetric_timoshenko}
\end{equation}
\added{Compared to \eqref{eq:symmetric_timoshenko}, the formulation of the shear strain contribution to the stiffness matrix shown in \eqref{eq:nonsymmetric_timoshenko} requires one less matrix operation. One can note that, due to the different choices of the function spaces for the shear stress and its variation, the global stiffness matrix is no longer symmetric.}

\paragraph{Remark} \added{ The symmetric \Bezier $\bar{B}$ formulation is not consistent with a mixed formulation. To see this we can recover the mixed formulation of \eqref{eqn:symmetric_b_bar_timoshenko_stiffness}, which is}
\begin{equation}
    \begin{bmatrix}
        \mathbf{K}^b & \hat{\mathbf{P}}^T \\
        sGA\hat{\mathbf{P}} & -\bar{\mathbf{M}}^{-1}
    \end{bmatrix},
\end{equation}
\added{where both the shear stress and its variation are discretized by the dual basis functions. However, for the inner product of dual basis functions }
\begin{equation}
    \langle{\hat{\bar{N}}_i,\hat{\bar{N}}_j}\rangle\neq{\bar{\mathbf{M}}^{-1}_{ij}},
\end{equation}
\added{which shows the inconsistency between the symmetric \Bezier $\bar{B}$ formulation and the mixed formulation.}

@@

and the term of this summation that results in the coupling between $N_{1}$ and $N_{5}$ is $\mathbf{P}_1^T\bar{\mathbf{M}}_2\mathbf{P}_3$, where $\mathbf{P}_1$ is the inner product of $N_{1}$ and $\hat{\bar{N}}_{2}$, $\mathbf{P}_3$ is the inner product of $N_{5}$ and $\hat{\bar{N}}_{3}$, and $\bar{\mathbf{M}}_2$ is the inner product of $\bar{N}_{2}$ and $\bar{N}_{3}$. We can see from Figure~\ref{fig:IGAelement} that $\operatorname{supp}(N_{1})\cap{}\operatorname{supp}(\hat{\bar{N}}_{2})=\Omega_1$, $\operatorname{supp}(N_{5})\cap{}\operatorname{supp}(\hat{\bar{N}}_{3})=\Omega_3$ and $\operatorname{supp}(\bar{N}_{2})\cap{}\operatorname{supp}(\bar{N}_{3})=\Omega_2$, so that $\mathbf{P}_1^T\bar{\mathbf{M}}_2\mathbf{P}_3$ is not zero. Thus we have increased the number of nonzero coefficients in the shear stiffness matrix. However, the same exercise can be used to show that there is no coupling between $N_{0}$ and $N_{6}$ for this set of basis functions so matrix is not dense. \added{With the abscense of the gramian matrix in the formulation of the shear stiffness matrix, the bandwidth of the non-symmetric B\'ezier $\bar{B}$ method is reduced further.} In fact, from the formulation of the element stiffness matrix, we can show that the bandwidth of the stiffness matrix of the symmetric B\'ezier $\bar{B}$ and non-symmetric B\'ezier $\bar{B}$ methods for the Timoshenko beam are $6p-3$ and $4p-1$, respectively.

@@

\added{In the context of nearly incompressible elasticity, the pressure $p$ can be viewed as an independent unknown, leading to a mixed formulation, as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ and $p\in{L}^2(\Omega)$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$ and $\delta{p}\in{L}^2(\Omega)$}

@@

Following the same pattern as the non-symmetric \Bezier $\bar{B}$ method for the Timoshenko beam problem, we keep the discretization of $\mathbf{u}$ and $\mathbf{w}$ untouched, while using lower order spline basis functions and corresponding dual basis functions for the discretization of pressure $p$ and its variation $\delta{p}$, respectively. The discretized stiffness matrix in mixed form can be written as
\begin{equation}
    \mathbf{K}_{mix}=
    \begin{bmatrix}
        \mathbf{K}^{dev} & -\mathbf{P}^{T}\\
        -\hat{\mathbf{P}} & -\dfrac{1}{(\lambda+2\mu/3)}\mathbf{I}
    \end{bmatrix},
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e^{vol},
\end{equation}
with
\begin{equation}
    \mathbf{P}_e^{vol}=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^{vol}_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
By eliminating the pressure control points, we obtain the pure displacement formulation as
\begin{equation}
	\mathbf{K} = \mathbf{K}^{dev} + \bar{\mathbf{K}}^{vol}_{NS},
\end{equation}
where
\begin{equation}
    \bar{\mathbf{K}}^{vol}_{NS}=(\lambda+2\mu/3){\mathbf{P}}^T\hat{\mathbf{P}}.
\end{equation}
We note, that in contrast to the symmetric \Bezier $\bar{B}$ method, the assembly of the stiffness matrix in this case can be performed in the standard way with no need for global matrix operations.

>>>>

\begin{abstract}
  In this paper we demonstrate the use of B\'{e}zier projection to alleviate locking phenomena in structural mechanics applications of isogeometric analysis. \added{Interpreting the well-known $\bar{B}$ projection in two different ways we develop two formulation for locking problems in beams and nearly incompressible elastic solids.  One formulation leads to a sparse symmetric symmetric system and the other leads to a sparse non-symmetric system.} To demonstrate the utility of the \added{\Bezier projection} for both geometry and material locking phenomena we focus on transverse shear locking in Timoshenko beams and volumetric locking in nearly compressible linear elasticity although the approach can be applied generally to other types of locking phenemona as well. B\'{e}zier projection is a local projection technique with optimal approximation properties, which in many cases produces solutions that are comparable to global $L^2$ projection. In the context of $\bar{B}$ methods, the use of B\'ezier projection produces sparse stiffness matrices with only a slight increase in bandwidth when compared to standard displacement-based methods. Of particular importance is that the approach is applicable to any spline representation that can be written in B\'ezier form like NURBS, T-splines, LR-splines, etc. We discuss in detail how to integrate this approach into an existing finite element framework with minimal disruption through the use of B\'ezier extraction operators and a newly introduced dual \added{basis for} the \Bezier \added{projection} operator. We then demonstrate the behavior of the two proposed formulations through several challenging benchmark problems.
\end{abstract}
\keywords{Isogeometric analysis, B\'ezier extraction, \added{\Bezier dual basis}, B\'ezier projection, $\bar{B}$-projection, locking}
\section{Introduction}
Isogeometric analysis (IGA), introduced by Hughes et al. \cite{hughes_isogeometric_2005}, adopts the spline basis, which underlies the CAD geometry, as the basis for analysis. Of particular importance is the positive impact of smoothness on numerical solutions, where, in many application domains, IGA outperforms classical finite elements~\cite{cottrell_isogeometric_2009,cottrell_studies_2007,cottrell2006isogeometric,hughes_duality_2008,bazilevs_isogeometric_2010,evans_n-widths_2009}. Initial investigations of IGA focused on non-uniform rational B-splines (NURBS) due to their dominance in commercial CAD packages. However, many advances are being made in analysis-suitable geometry representations that overcome the strict rectangular topological restrictions of NURBS. Examples include T-splines~\cite{bazilevs_isogeometric_2010,sederberg_t-splines_2003} and their analysis-suitable restriction~\cite{scott_local_2012, li_analysis-suitable_2013}, hierarchical B-splines~\cite{bornemann_subdivision-based_2013,scott_isogeometric_2014,schillinger_isogeometric_2012,evans_hierarchical_2015,forsey_hierarchical_1988}, and locally refined B-splines~\cite{dokken_polynomial_2013,johannessen_isogeometric_2014} among others.

@@

\added{In this paper we introduce two methods that employ \Bezier projection to produce a localized approximation to the standard $\bar{B}$ method. The motivation behind these methods is the fact that $\bar{B}$ methods result in dense linear systems when used in the context of smooth higher-order basis functions, for example NURBS or other splines. The methods we introduce result in a sparse linear system irrespective of the choice of basis functions. We call these methods the symmetric and non-symmetric \Bezier $\bar{B}$ projection methods, where the names indicate the symmetry of the resulting stiffness matrix. We show that both methods result in a sparse stiffness matrix and reduce locking. We also show that optimal convergence rates are achieved in the case of the non-symmetric method and near optimal convergence rates are achieved in the case of the symmetric method.  We also perform an inf-sup analysis of these methods.}

@@

The element-wise projection produces one control value for each element in the support of the function.  These values must be combined in order to provide the final control value.  A core component of the B\'ezier projection algorithm is the definition of an appropriate averaging operation. \added{The process of computing the weights is illustrated in Figure~\ref{fig:weights}.} A weighted average of the values is computed using the weighting
\begin{equation}\label{eqn:Bezier_weight}
\omega_a^e=\dfrac{\int_{\Omega^e} N_{a}^e \, d\Omega}{\int_{\Omega^A} N_{A(e,a)} \, d\Omega}
\end{equation}
where $\Omega^e$ corresponds to the physical domain of element $e$, $A(e,a)$ is a mapping from a local nodal index $a$ defined over element $e$ to a corresponding global node index $A$, and $\Omega^A$ corresponds to the physical support of $N_A$. The final averaged global control point is then calculated as
\begin{equation}
P_A=\sum_{\Omega^e\in \Omega^A } \omega_{A(e,a)} P_{A(e,a)}.
\end{equation}
B\'ezier projection onto NURBS functions can be defined in an analogous manner~\cite{thomas_bezier_2015}.

@@

\subsection{Dual basis formulation of B\'{e}zier projection}
\label{sec:dual-funct-dual}
To integrate \Bezier projection into a standard finite element assembly algorithm, it is convenient to recast \Bezier projection in terms of a dual basis. 
%\added{This approach plays a key role in developing the non-symmetric \Bezier $\bar{B}$ method discussed in Section~\ref{sec:non-symmetric}.} 
A dual basis has the distinguishing property that
\begin{align}
  \int_{\Omega} \hat{N}_A N_B \, d\Omega = \delta_{AB}.
  \end{align}
Once a dual basis is defined it can be processed in much the same manner as standard basis functions are processed in a finite element code. A complete exposition on the subject of dual bases and the \Bezier projection framework can be found in~\cite{thomas_bezier_2015}. We first define the dual element extraction operator
\begin{align}
 \hat{\mathbf{D}}^e=\operatorname{diag}({\boldsymbol{\omega}^e})\mathbf{R}^e(\mathbf{G}^e)^{-1}
\end{align}
where $\mathbf{G}^e$ is the Gramian matrix of the Bernstein basis functions over the element and $\operatorname{diag}({\boldsymbol{\omega}^e})$ is a diagonal matrix that contains the B\'ezier projection weights computed by (\ref{eqn:Bezier_weight}). We can then define a dual basis function $\hat{N}_{A(e,a)}$ restricted to element $e$ as
\begin{align}
\hat{N}^e_{a} = \sum_{j}\hat{D}_{aj}^e B_{j}.
\label{eq:local-dual-basis}
\end{align}

@@

\subsection{Symmetric \Bezier $\bar{B}$ projection}
\label{sec:symmetric-projection}
{\color{blue}Locking is caused in Timoshenko beam problems by the transverse shear. To reduce the effects of locking for these problems the $\bar{B}$ method projects the shear strain, $\gamma$, onto a lower order function space. This process produces a projected shear strain, which we call $\bar{\gamma}$,  that is substituted into the weak form of the problem statement. In this section we use the \Bezier projection operator to compute an approximation of $\bar{\gamma}$, and refer to this approach as the symmetric \Bezier $\bar{B}$ projection method because the resulting stiffness matrix is symmetric.}

@@

\subsubsection{Discretization}
\added{We discretize $\omega$ and $\phi$ as}
\begin{align}
  \added{\omega = \sum_A \omega_A N_A} \\
  \added{\phi = \sum_A \phi N_A}
\end{align}
where \added{$N_A$ is a degree $p$ spline basis function and $\omega_A$ and $\phi_A$ are the corresponding control point values. The shear strain and bending strain can then be expressed as}
{\color{blue}\begin{align}
\gamma &= \sum_A{\begin{bmatrix}N'_A & -N_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T} \\
\kappa &= \sum_A\begin{bmatrix}0 & N'_A\end{bmatrix}\begin{bmatrix}\omega_A & \phi_A\end{bmatrix}^T
\end{align}}
The shear strain $\bar{\gamma}$ is constructed by B\'{e}zier projection of the true shear strain $\gamma$ onto a lower degree space. In other words, we project from a $p^{th}$ degree spline space with $n$ basis functions $\mathbf{N}$ defined by the knot vector
\begin{align}
\mathbf{\Xi}_{p}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p+1$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p+1$ copies}}\rbrace,
\label{eq:origin_knot_vector}
\end{align}
onto a $p-1^{th}$ degree spline space with $\bar{n}$ basis functions $\bar{\mathbf{N}}$ defined by the knot vector
\begin{equation}
\bar{\mathbf{\Xi}}_{p-1}=\lbrace{\underbrace{0,0,\ldots,0}_\text{$p$ copies}},\mathbf{\Xi}_{int},{\underbrace{1,1,\ldots,1}_\text{$p$ copies}}\rbrace
\label{eq:projected_knot_vector}
\end{equation}
where the internal knots, denoted by $\mathbf{\Xi}_{int}$, are the same for both spaces. The projected shear strain $\bar{\gamma}$ can then be written as
\begin{align}
  \bar{\gamma} &= \sum_A \bar{\gamma}_A \bar{N}_A.
\end{align}
The control variables $\bar{\gamma}_A$ are simply
\begin{align}
  \bar{\gamma}_A = \int_{\Omega^A} \hat{\bar{N}}_A \gamma \, d\Omega = \langle \hat{\bar{N}}_A, \gamma \rangle_{\Omega^i}
\end{align}
where $\hat{\bar{N}}_A$ is a dual basis function for the spline space of degree $p-1$ computed from \eqref{eq:local-dual-basis}.

@@

\added{Simo and Hughes \cite{hughes_variational_1986} have shown that $\bar{B}$ formulations and mixed formulations are equivalent. However, the development of the symmetric \Bezier $\bar{B}$ projection method presented in Section~\ref{sec:symmetric-projection}, where we began by considered the $\bar{B}$ formulation as a strain projection method, lacks a connection to mixed formulations. In this section we present a second method based on \Bezier projection in which we view the $\bar{B}$ formulation as a mixed formulation where, for the Timoshenko beam problem, the auxiliary variable is the shear strain.  In this method we use the \Bezier dual basis functions as the test functions for the auxiliary variable. Once the problem has been cast as a mixed formulation we then eliminate the auxiliary variable to get a purely displacement based formulation. This method preserves convergence rates and all assembly routines of the stiffness matrix can be performed at the element level, but it does lead to a non-symmetric stiffness matrix.}

\subsubsection{The weak form}
\added{In the mixed formulation for the Timoshencko beam problem the shear stress, $\tau=sGA\gamma$, is taken as a new independent variable. The weak form of the mixed formulation problem is then stated as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ and $\tau\in{L}^2(\Omega)$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$ and $\delta\tau\in{L}^2(\Omega)$}
\begin{align}
    \int_{0}^L\kappa(\mathbf{w})EI\kappa(\mathbf{u}) + {\gamma}(\mathbf{w})\tau \, dx&= l\langle{\mathbf{w}}\rangle\\
    \int_{0}^L\delta\tau(sGA\gamma(\mathbf{u})-\tau) \, dx &= 0.
\end{align}
\subsubsection{Discretization}
\added{In the finite element formulation of the mixed problem the discretization of $\mathbf{u}$ and $\mathbf{w}$ remain the same. The shear strain and its variation, however, are in $L^2(\Omega)$, so their finite element approximation can be made from functions with lower regularity, such as discontinuous polynomials. When the field $\mathbf{u}$ is discretized by $p^{th}$ degree spline basis functions defined by the knot vector given in \eqref{eq:origin_knot_vector}, we chose the $p-1^{th}$ degree spline basis functions defined by the knot vector given in \eqref{eq:projected_knot_vector} to discretize the shear stress $\tau$ and the corresponding dual basis to discretize its variation $\delta\tau$. The discrete form of the shear stress and its variation are given by}
\begin{align}
    \tau&=\sum_A\tau_A\bar{N}_A \\
    \delta\tau&=\sum_A\delta\tau_A\hat{\bar{N}}_A.
\end{align}
\added{The stiffness matrix for the mixed form can then be written as}
\begin{equation}
   \mathbf{K}_{mix} =  
    \begin{bmatrix}
        \mathbf{K}^b & \mathbf{P}^T \\
        sGA\hat{\mathbf{P}} & -\mathbf{I}
    \end{bmatrix}
    \label{eq:mixed_timoshenko}
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e,
\end{equation}
\added{and}
\begin{equation}
    \mathbf{P}_e=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
\added{We can now eliminate the control variable of the shear stress from \eqref{eq:mixed_timoshenko} to get a pure displacement formulation where the stiffness matrix can be written as}
\begin{equation}
    \mathbf{K}=\mathbf{K}^b+\bar{\mathbf{K}}^s_{NS}, 
\end{equation}
where 
\begin{equation}
    \bar{\mathbf{K}}^s_{NS}=sGA\mathbf{P}^T\hat{\mathbf{P}}.
    \label{eq:nonsymmetric_timoshenko}
\end{equation}
\added{We can see that use of different function spaces for the shear strain and its variation leads to a non-symmetric stiffness matrix.}

\paragraph{Remark} \added{ The symmetric \Bezier $\bar{B}$ formulation is not consistent with a mixed formulation. To see this we can recover the mixed formulation of \eqref{eqn:symmetric_b_bar_timoshenko_stiffness}, which is}
\begin{equation}
    \begin{bmatrix}
        \mathbf{K}^b & \hat{\mathbf{P}}^T \\
        sGA\hat{\mathbf{P}} & -\bar{\mathbf{M}}^{-1}
    \end{bmatrix},
\end{equation}
\added{where both the shear stress and its variation are discretized by the dual basis functions. However, for the inner product of dual basis functions we have}
\begin{equation}
    \langle{\hat{\bar{N}}_i,\hat{\bar{N}}_j}\rangle\neq{\bar{\mathbf{M}}^{-1}_{ij}},
\end{equation}
\added{which shows the inconsistency between the symmetric \Bezier $\bar{B}$ formulation and the mixed formulation.}

@@

and the term of this summation that results in the coupling between $N_{1}$ and $N_{5}$ is $\mathbf{P}_1^T\bar{\mathbf{M}}_2\mathbf{P}_3$, where $\mathbf{P}_1$ is the inner product of $N_{1}$ and $\hat{\bar{N}}_{2}$, $\mathbf{P}_3$ is the inner product of $N_{5}$ and $\hat{\bar{N}}_{3}$, and $\bar{\mathbf{M}}_2$ is the inner product of $\bar{N}_{2}$ and $\bar{N}_{3}$. We can see from Figure~\ref{fig:IGAelement} that $\operatorname{supp}(N_{1})\cap{}\operatorname{supp}(\hat{\bar{N}}_{2})=\Omega_1$, $\operatorname{supp}(N_{5})\cap{}\operatorname{supp}(\hat{\bar{N}}_{3})=\Omega_3$ and $\operatorname{supp}(\bar{N}_{2})\cap{}\operatorname{supp}(\bar{N}_{3})=\Omega_2$, so that $\mathbf{P}_1^T\bar{\mathbf{M}}_2\mathbf{P}_3$ is not zero. Thus we have increased the number of nonzero coefficients in the shear stiffness matrix. However, the same exercise can be used to show that there is no coupling between $N_{0}$ and $N_{6}$ for this set of basis functions so the matrix is not dense. \added{the bandwidth of the non-symmetric B\'ezier $\bar{B}$ method is reduced further. This is because the Gramian matrix does not appear in the this formulation.} In fact, from the formulation of the element stiffness matrix, we can show that the bandwidth of the stiffness matrix of the symmetric B\'ezier $\bar{B}$ and non-symmetric B\'ezier $\bar{B}$ methods for the Timoshenko beam are $6p-3$ and $4p-1$, respectively.

@@

\added{A mixed formulation for nearly incompressible elasticity can be developed by considering the pressure $p$ as an independent variable. The weak statement of the problem is then given as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ and $p\in{L}^2(\Omega)$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$ and $\delta{p}\in{L}^2(\Omega)$}

@@

Following the same pattern as the non-symmetric \Bezier $\bar{B}$ method for the Timoshenko beam problem, we use the same discretization for $\mathbf{u}$ and $\mathbf{w}$ and use lower order spline basis functions and corresponding dual basis functions for the discretization of pressure $p$ and its variation $\delta{p}$, respectively. The discretized stiffness matrix in mixed form can be written as
\begin{equation}
    \mathbf{K}_{mix}=
    \begin{bmatrix}
        \mathbf{K}^{dev} & -\mathbf{P}^{T}\\
        -\hat{\mathbf{P}} & -\dfrac{1}{(\lambda+2\mu/3)}\mathbf{I}
    \end{bmatrix},
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e^{vol},
\end{equation}
with
\begin{equation}
    \mathbf{P}_e^{vol}=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^{vol}_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
By eliminating the pressure control variables, we obtain a pure displacement formulation with the stiffness matrix taking the form
\begin{equation}
	\mathbf{K} = \mathbf{K}^{dev} + \bar{\mathbf{K}}^{vol}_{NS},
\end{equation}
where
\begin{equation}
    \bar{\mathbf{K}}^{vol}_{NS}=(\lambda+2\mu/3){\mathbf{P}}^T\hat{\mathbf{P}}.
\end{equation}
We note again, that in contrast to the symmetric \Bezier $\bar{B}$ method, the assembly of the stiffness matrix in this case can be performed in the standard way with no need for global matrix operations.
